Implementing simplified INLA into `aghq`

### 2022-10-26 src/dev_sinla/sinla.Rmd
Try bug resolve by using rlang::duplicate and being careful, note on tmbstan #16

It is simple to fit the model using MCMC via the `tmbstan` package.
We use 4 `chains` each of 5000 `iter`:

@@

#' Note that I'm calling this mean, but because it's a Gaussian the mean is the same as the mode
mean <- mm[h$env$random]
length(mean) #' The length is 30

#' Hessian evaluated at the mean (or equivalently mode)
Q <- h$env$spHess(mm, random = TRUE)
dim(Q) #' With dimension [30 x 30]
```

@@

```{r}
#' Making sure the mean and Q used here are correct (preventing and shady TMB behaviour)
h$fn(opt_theta)
mm <- h$env$last.par
mean <- mm[h$env$random]
Q <- h$env$spHess(mm, random = TRUE)

i <- 1
mean_i <- as.numeric(mean[i])
var_i <- solve(Q)[i, i]
```

@@

```{r}
mm <- obj$env$last.par
mean <- mm[obj$env$random]
length(mean) #' The length is 30 - 1

Q <- obj$env$spHess(mm, random = TRUE)
dim(Q) #' With dimension [(30 - 1) x (30 - 1)]
```

@@

```{r}
xi_laplace_marginal <- function(i) {
  dat_i <- prepare_dat(dat, i)
  map_fixed_theta <- list(beta_prev = factor(NA), log_sigma_phi_prev = factor(NA))
  param_i_fixed_theta <- list(beta_prev = 0, phi_prev_i = 0, phi_prev_minus_i = rep(0, data$n - 1), log_sigma_phi_prev = 0)
  for(theta in names(opt_theta$par)) param_i_fixed_theta[[theta]] <- opt_theta$par[[theta]]
  obj_fixed_theta <- MakeADFun(data = dat_i, parameters = param_i_fixed_theta, random = "phi_prev_minus_i", DLL = "model1index", silent = TRUE, map = map_fixed_theta)
  quad <- aghq::aghq(ff = obj_fixed_theta, k = 3, startingvalue = 0, control = aghq::default_control_tmb())
  pdf_and_cdf <- aghq::compute_pdf_and_cdf(quad)[[1]]
  return(pdf_and_cdf)
}

>>>>

It is simple to fit the model using MCMC via the `tmbstan` package.
We use 4 `chains` each of 5000 `iter`.
Note that although `h` is passed to `tmbstan::tmbstan`, the Laplace approximation is disabled by setting `laplace = FALSE` by default (useful to know in case it's ever of interest to sample from the Laplace approximation).

@@

#' Note that I'm calling this mean, but because it's a Gaussian the mean is the same as the mode
x_mean <- mm[h$env$random]
x_mean <- rlang::duplicate(x_mean) #' Insurance...
length(x_mean) #' The length is 30

#' Hessian evaluated at the mean (or equivalently mode)
x_Q <- h$env$spHess(mm, random = TRUE)
x_Q <- rlang::duplicate(x_Q)
dim(x_Q) #' With dimension [30 x 30]
```

@@

```{r}
i <- 1
mean_i <- as.numeric(x_mean[i])
var_i <- solve(x_Q)[i, i]
```

@@

```{r}
get_mean_and_Q <- function(obj) {
  mm <- obj$env$last.par
  mean <- mm[obj$env$random]
  mean <- rlang::duplicate(mean)
  Q <- obj$env$spHess(mm, random = TRUE)
  Q <- rlang::duplicate(Q)
  return(list(mean = mean, Q = Q))
}

xminusi <- get_mean_and_Q(obj)
```

@@

```{r}
xi_laplace_marginal <- function(i) {
  dat_i <- prepare_dat(dat, i)
  map_fixed_theta <- list(beta_prev = factor(NA), log_sigma_phi_prev = factor(NA))

  param_i_fixed_theta <- list(
    beta_prev = 0, 
    phi_prev_i = 0, 
    phi_prev_minus_i = rep(0, data$n - 1), 
    log_sigma_phi_prev = 0
  )

  for(theta in names(opt_theta$par)) param_i_fixed_theta[[theta]] <- opt_theta$par[[theta]]

  obj_fixed_theta <- MakeADFun(
    data = dat_i,
    parameters = param_i_fixed_theta,
    random = "phi_prev_minus_i",
    DLL = "model1index",
    silent = TRUE,
    map = map_fixed_theta
  )

  quad <- aghq::aghq(ff = obj_fixed_theta, k = 3, startingvalue = 0, control = aghq::default_control_tmb())
  pdf_and_cdf <- aghq::compute_pdf_and_cdf(quad)[[1]]

  return(pdf_and_cdf)
}
